Binding of cations to phospholipid bilayers

### 2015-02-16 LIPIDionINTERACT/LIPIDionINTERACT.tex
update lipid-ion manuscript

%The experimental results~\cite{akutsu81}, plotted in Fig.~\ref{ordPions} shows a distinct difference
%in behaviour as a function of ions: the choline order parameters were unaffected by the addition of NaCl, 
%whereas a systematic decrease was observed by the addition of CaCl$_2$. Following the electrometer
%concept this means that the binding constant for divalent Ca$^{2+}$ is higher than for monovalent Na$^+$
%which is in line with the large amount of experimental data with different techniques~\cite{cevc90,binder02,petrache06,pabst07,filippov09}.
\begin{figure}[]
  \centering
  \includegraphics[width=8cm]{OrderParameterIONSchanges.eps}
  \caption{\label{ordPions}
    The change of order parameters for $\beta$ and $\alpha$ segments as a function of NaCl (left column) and CaCl$_2$ (right column) concentrations from simulations 
    and experiments by Akutsu et al.~\cite{akutsu81}. The signs of the order parameters without ions are taken from~\cite{hong95a,hong95b,gross97} and it is reasonable
    to assume that the sign do not change with concentrations repsented here~\cite{altenbach84}. Note that the $\beta$ order parameter with negative sign decreases here with cation
    penetration in contrast to measured absolute value increase in the origical studues~\cite{akutsu81,altenbach84}.
    Regarding the actual electrometer concept this not relevant, however. 
    The experimental accuracy of order parameter changes is much higher than the accuracy of quantitative values due to high resolution of $^2$H NMR spectroscopy~\cite{??}. 
   }
\todo{I think that we have to run Orange simulation with higher NaCl concentration. I will do it.} \\
\todo{I think that we have to run CHARMM36 with CaCl$_2$. If anyone happen to have the data and is willing to share,
let us know. If not, then I will do it.} \\
\todo{ I think that it would be very interesting to test the modified CHARMM ions: Venable et al. dx.doi.org/10.1021/jp401512z, J. Phys. Chem. B 2013, 117, 10183−10192.
According to the paper, these parameters improve the ion binding to the charged lipid bilayers. Even though I think that testing this would be highly relevant, I do not have
time to do it now.}
\end{figure}

>>>>

%The experimental results~\cite{akutsu81}, plotted in Fig.~\ref{ordPions} shows a distinct difference
%in behaviour as a function of ions: the choline order parameters were unaffected by the addition of NaCl, 
%whereas a systematic decrease was observed by the addition of CaCl$_2$. Following the electrometer
%concept this means that the binding constant for divalent Ca$^{2+}$ is higher than for monovalent Na$^+$
%which is in line with the large amount of experimental data with different techniques~\cite{cevc90,binder02,petrache06,pabst07,filippov09}.
\begin{figure}[]
  \centering
  \includegraphics[width=8cm]{OrderParameterIONSchanges.eps}
  \caption{\label{ordPions}
    The change of order parameters for $\beta$ and $\alpha$ segments as a function of NaCl (left column) and CaCl$_2$ (right column) concentrations from simulations 
    and experiments by Akutsu et al.~\cite{akutsu81}. The signs of the order parameters without ions are taken from~\cite{hong95a,hong95b,gross97} and it is reasonable
    to assume that the sign do not change with concentrations repsented here~\cite{altenbach84}. Note that the $\beta$ order parameter with negative sign decreases here with cation
    penetration in contrast to measured absolute value increase in the origical studues~\cite{akutsu81,altenbach84}.
    Regarding the actual electrometer concept this not relevant, however. 
    The experimental accuracy of order parameter changes is much higher than the accuracy of quantitative values due to high resolution of $^2$H NMR spectroscopy~\cite{??}. 
   }
\todo{The ion concentrations for, at least, Berger, CHARMM36 and Orange has to be recalculated, see http://nmrlipids.blogspot.com/2015/02/the-first-draft-of-ion-lipid.html?showComment=1423771449743\#c5884666173819273918 \\
 I think that we have to run Orange simulation with higher NaCl concentration. I will do it.} \\
\todo{I think that we have to run CHARMM36 with CaCl$_2$. If anyone happen to have the data and is willing to share,
let us know. If not, then I will do it.} \\
\todo{ I think that it would be very interesting to test the modified CHARMM ions: Venable et al. dx.doi.org/10.1021/jp401512z, J. Phys. Chem. B 2013, 117, 10183−10192.
According to the paper, these parameters improve the ion binding to the charged lipid bilayers. Even though I think that testing this would be highly relevant, I do not have
time to do it now.}
\end{figure}
